Sampling requirements to detect ecosystem change

### 2020-01-04 R/temporal-sampling.Rmd
added new theoretical results section

We then explored how each of these model components affected our ability to detect a change point. We simulate an entire time series, but we also examine the effect of not sampling every year. We specifically study how the amount of samples included and the type of sampling affects the detection probability. In particular, we examine three types of sampling: random, regular, and iterative.

```{r theoretical_results, fig.cap='Theoretical results here',message=F,warning=F,echo=F}
# 4(or 6?) panel plot
## Example time series
## Changepoint detection vs number of samples - maybe just stick with regular sampling
## Number of samples required vs shift size, shift time, variance, autocorrelation

@@

>>>>

We then explored how each of these model components affected our ability to detect a change point. We simulate an entire time series (the "true" data for comparison), but we also examine the effect of not sampling every year. We specifically study how the amount of samples included and the type of sampling affects the detection probability. In particular, we examine three types of sampling: random, regular, and iterative.

```{r old_theoretical_results, fig.cap='Theoretical results here',message=F,warning=F,echo=F,eval=F}
# 4(or 6?) panel plot
## Example time series
## Changepoint detection vs number of samples - maybe just stick with regular sampling
## Number of samples required vs shift size, shift time, variance, autocorrelation

@@

```{r theoretical_results, fig.cap='Theoretical results here',message=F,warning=F,echo=F,eval=F}

source('R/sampling_regular.R')
source('R/build_time_series.R')
source('R/updated_param_sensitivity.R')

par(mfrow=c(2,2))
# Sigma plot
sample_size=10

sigma15 <- param_sensitivity('sigma',15)

plot(sigma15,ylab='Probability correct',xlab='sigma',pch=16,cex.lab=1.3,las=1,ylim=c(0,1),col=1)
